A preliminary constraint grammar for Russian

### 2015-02-18 2015-nodalida-ruscg/ruscg.tex
stuff
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58852 72bbbca6-d526-0410-a7d9-f06f51895060
more stuff
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58998 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{times}
\usepackage{latexsym}
\usepackage{fixltx2e} %allows subscripts
%\usepackage{mathptmx}
%\usepackage{txfonts}
\usepackage{url}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

@@

@@

\begin{table}
  \begin{tabular}{lrrr}
    \hline
         & {\sc select} & {\sc remove} & {\sc map} \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \begin{tabular}{|l|r|r|}
    \hline
    Missing lexeme & &  \\          % безбалластный, FALSENEG: Кий<np><ant><m><sg><ins> ['кий<n><m><nn><sg><ins>']
    Partial lexeme & &  \\          % франко-норманнское
    Missing analysis & &  \\        % 
    Equally valid analysis & & \\   % большой<adj><comp><pred> ['больше<adv>'] (?)
    Correct reading removed & &  \\ % 
    \hline
  \end{tabular}

\end{table}

>>>>

\usepackage{times}
\usepackage{latexsym}
\usepackage{fixltx2e} %allows subscripts
%\usepackage{mathptmx}
%\usepackage{txfonts}
\usepackage{url}
\usepackage[small,bf]{caption}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

% objectives:
%% make a free/open-source morphology for russian based on Z's dictionary that includes stress

@@

\cite{yablonsky1999russian}

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \hline
         & {\sc select} & {\sc remove} & {\sc map} \\
    Safe & & & \\
    Safe heuristic  & & & \\
    Heuristic &  & & \\
    Syntax labelling &  &   & \\ 
    \hline
  \end{tabular}
  \caption{Rules in the grammar are separated into four sections. }
\end{table}

@@

\begin{table*}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    \textbf{Domain} & \textbf{Tokens} & \textbf{Precision} & \textbf{Recall} & \textbf{Ambig. solved} \\
    \hline
    Wikipedia       & 7,857      & 0.506        & 0.996    & 44.92\%  \\
    News            & 642        & 0.471        & 0.990    & 41.60\%  \\
    Literature      & 1,652      & 0.473        & 0.984    & 42.95\%  \\
    \hline
    Total           & 10,150     & 0.498        &  0.994   &  44.39\% \\
    \hline
  \end{tabular}
  \caption{Results for the test corpora.}
\end{table*}

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|}

    \hline
    Error in original        &   & 2 \\
    Missing lexeme           &   & 8  \\          % безбалластный, FALSENEG: Кий<np><ant><m><sg><ins> ['кий<n><m><nn><sg><ins>']
    Partial lexeme           &   & 2  \\          % франко-норманнское, рельс
    Missing analysis         &   &    \\        % 
    Equally valid analysis   &   &    \\   % большой<adj><comp><pred> ['больше<adv>'] (?)
    Correct reading removed  &   & 34   \\ % 
    \hline
                             &   & 46 \\
    \hline
  \end{tabular}
  \caption{Error analysis of false negatives}
\end{table}
